Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-07 article.tex
add : explication in proof of lemma 2
modification : the proof of lemma 2

\begin{lemma}
\label{lemma:MatchStripeToPermutation}
Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations. Then $\pi$ contains $\sigma$ by a subsequence $s$ if and only if $s_\sigma$ is a subsequence of $s_\pi$ by the same subsequence $s$.
\end{lemma}

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation. Same goes for the permutation $(21)$. Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$. Suppose that there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$, Let's $s$ be the subsequence such that $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$.
	By induction $\pmotif[2:]$ appears in $\ptext$ by subsequence $s[2:]$.
	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif. Furthermore $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$ by subsequence $s$, so $\stripe{s}{1}$ is also ascend (descent) thus $s[1]$ is also the minimal (maximal) element of the subsequence $s$ which complete our proof.
\qed
\end{proof}

>>>>

\begin{lemma}
\label{lemma:MatchStripeToPermutation}
Let $\pi$ and $\sigma$ be two $(213,231)$-avoiding permutations, given a subsequence $t$ of $\ptext$, $t$ is an occurrence of $\pmotif$ in $\ptext$ if and only if $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$.
\end{lemma}

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$. Because we have $\stripe{t}{1}=\ustep$, so the next element of $t[1]$ in $\ptext$ is superior to  $t[1]$, so we have a match. Same idea goes of motif $(21)$.
	Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Suppose that we have a subsequence $t$ of $\ptext$ such that $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$, then $\stripew{t[2:]}$ is an occurrence of $\pmotif[2:]$ in $\ptext$. Moreover
	$\pmotif[2:] \in \Av{n}{(231,213)}$ so by hypothesis of induction $t[2:]$ is an occurrence of $\sigma[2:]$ in $\ptext$.
	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif. Furthermore $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$ , so $\stripe{t}{1}$ is also ascend (descent) thus $t[1]$ is also the minimal (maximal) element of the subsequence $t$ which complete our proof.

\qed
\end{proof}
